### 2017-06-05 paper.tex
A series of minor fixes to remove typos and jargon

Thousands of university lecturers teach subjects ranging from first year biology,
to graduate-level courses in Indian film.
Some might use a common textbook written by a single author or two,
but other than that they usually develop and improve their course materials in isolation.
It is staggering to think how many wheels are being re-invented,
how the progress of teaching in these fields has been held back by
the lack of community collaboration and sharing,
and how much valuable time has been wasted.

This problem extends beyond university teaching,
but it is curious that it is endemic in tertiary education,
given that research depends so critically on collaboration and sharing,
and that most researchers complain about how much time teaching takes away from research.

@@

By definition,
open education projects satisfy the first criterion,
but very few satisfy the second:
while their lessons might occasionally be updated by a small author group,
as happens when a new edition of a book is edited and published,
this is not the same as continuous improvement by a large community of contributors.
The ten simple rules that follow summarize what we have learned about doing that
as maintainers, editors, and reviewers of lessons used by tens of thousands of people.

@@

Note that doing this shifts the instructor's burden from writing to finding and synthesizing.
Both of which are easier if lessons have been designed by people with a shared world-view (Rule~6),
and if lessons clearly signal what they cover (Rule~1).
In particular,
if lessons reference specific points in the model curriculum guidelines promulgated by many professional societies,
it can be much easier for people to find them and integrate them.

@@

Tools can help,
especially if they support pre-merge review.
Yet some of these tools come with a considerable up-front learning curve.
GitHub with pull requests may be ideal,
but allowing people to edit a Google Doc,
or to facilitate Wiki-based editing,
can help get conversations started.
In a pinch,
work with contributors to find a comfort zone:
don't let a collaboration flounder on technological choice.
But make sure not to overwhelm either:
threaded discussion (or GitHub issues) will help increase the signal-to-noise ratio.

@@

Academia has only a few ways of recognizing contributions.
Until these are expanded,
it is important to publish lessons in ways that traditional academic systems can digest.
One is to give particular releases of lessons
DOIs supplied by providers such as Zenodo (\url{https://zenodo.org/})
or DataCite (\url{https://zenodo.org/}).
Contributors can be listed as authors
and the maintainers of the lesson as editors
to differentiate recognition of their contributions.
Each time the lesson is published,
names and (where possible) identifiers like ORCIDs
should also be gathered for all contributors.

@@

Pre- and post-class surveys can be used to discover larger macro-scale issues.
These issues often relate to the fact that it can be difficult for lesson developers
to fully understand the frame of reference of their audience.
For instance, a lesson might inadvertently assume prior knowledge that many learners don't have,
which is information that can be collected easily in a survey.
If possible, it's a good idea to conduct the post-class survey 30-60 days after the fact.
This allows people time to reflect,
meaning they are more likely to give accurate feedback on what they learned
rather than how entertained they were.

Pre- and post-class surveys also are essential in focusing in on the audience for a given lesson.
Referring back to Rule~1,
it can sometimes be difficult for lesson developers to understand the frame of a given learner
so surveys (particularly post-class surveys) can reveal hidden assumed knowledge
that can be expanded on or acknowledged to refine the target audience.

@@

Doing this is a lot of work,
and maintaining it is even more,
which makes building community around lessons (Rule~2) all the more important.
In particular,
it is vital to engage the learners as equal participants in that community:
they should both be able to propose updates, corrections, and additions to lessons,
and know that they are encouraged to do so (Rule~5).

>>>>

Thousands of university lecturers around the world teach subjects ranging from first year biology
to graduate-level courses in Indian film.
Some might use a common textbook written by a single author or two,
but besides that lecturers usually develop and improve their course materials in isolation.
It is staggering to think how many wheels have been re-invented,
how much valuable time has been wasted,
and ultimately how the progress of tertiary education has been held back by
the lack of community collaboration and sharing in this process.

This problem obviously extends beyond the university sector,
but it is curious that it is endemic in tertiary education,
given that research depends so critically on collaboration and sharing,
and that most researchers complain about how much time teaching takes away from research.

@@

By definition,
many open education projects satisfy the first criterion,
but very few satisfy the second:
while their lessons might occasionally be updated by a small author group,
as happens when a new edition of a book is edited and published,
this is not the same as continuous improvement by a large community of contributors.
The ten simple rules that follow summarize what we have learned about doing that
as maintainers, editors, and reviewers of lessons used by tens of thousands of people.

@@

Doing this shifts the instructor's burden from writing to finding and synthesizing,
both of which are easier if lessons have been designed by people with a shared world-view (Rule~6),
and if lessons clearly signal what they cover (Rule~1).
In particular,
if lessons reference specific points in the model curriculum guidelines promulgated by many professional societies,
it can be much easier for people to find them and integrate them.

@@

Tools can help,
especially if they allow proposed changes to be viewed and discussed
prior to their incorporation/merger into the lessons
(in open source software development this is known as ``pre-merge review'').
Yet some of these tools come with a considerable up-front learning curve.
GitHub with pull requests is ideal for pre-merge review, for instance,
but it requires contributors to understand the basics of the git version control software.
Allowing people to edit a Google Doc or Wiki-based editing does not offer pre-merge review,
but the low barrier to entry can help get conversations started.
In a pinch,
work with contributors to find a comfort zone:
don't let a collaboration flounder on technological choice.
But make sure not to overwhelm either:
threaded discussion on paticular topics (e.g. GitHub issues) can help increase the signal-to-noise ratio
by reducing long reply-all email excahnges.

@@

Academia has only a few ways of recognizing contributions.
Until these are expanded,
it is important to publish lessons in ways that traditional academic systems can digest.
One is to give particular releases of lessons
DOIs supplied by providers such as Zenodo (\url{https://zenodo.org/})
or DataCite (\url{https://www.datacite.org/}).
Contributors can be listed as authors
and the maintainers of the lesson as editors
to differentiate recognition of their contributions.
Each time the lesson is published,
names and (where possible) identifiers like ORCIDs
should also be gathered for all contributors.

@@

Pre- and post-class surveys can be used to discover larger macro-scale issues.
These issues often relate to the fact that it can be difficult for lesson developers
to fully understand the frame of reference of their audience.
For instance, a lesson might inadvertently assume prior knowledge that many learners don't have,
which is information that can be collected in a survey.
If possible, it's a good idea to conduct the post-class survey 30--60 days after the fact.
This allows people time to reflect,
meaning they are more likely to give accurate feedback on what they learned
rather than how entertained they were.

Pre- and post-class surveys also are essential in focusing in on the audience for a given lesson.
Referring back to Rule~1,
it can sometimes be difficult for lesson developers to understand the frame of a given learner,
so surveys (particularly post-class surveys) can reveal hidden assumed knowledge
that can be expanded on or acknowledged to refine the target audience.

@@

Doing this is a lot of work,
and maintaining it is even more so,
which makes building community around lessons (Rule~2) all the more important.
In particular,
it is vital to engage the learners as equal participants in that community:
they should both be able to propose updates, corrections, and additions to lessons,
and know that they are encouraged to do so (Rule~5).
